\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


% serif fonts
%\usepackage{CormorantGaramond}
\usepackage{charter}
%\usepackage{CrimsonPro}
%\usepackage{algolrevived}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% ---------
% doc start
% ---------
\begin{document}
\begin{center}
	\textbf{\Huge \scshape Felipe Farías } \\ \vspace{2pt}
	\small +56 9 3962 6293 $|$
    \href{mailto:felipe.farias.e1@gmail.com}{\underline{Felipe.Farias.e1@gmail.com}} $|$ 
	\href{https://www.linkedin.com/in/felipefa6/}{\underline{Linkedin.com/in/FelipeFa6}} $|$
	\href{https://github.com/FelipeFa6}{\underline{Github.com/FelipeFa6}}
\end{center}


% education 
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{University of Helsinki}{Remote}
{Full stack Open Certification}{2024}
\resumeSubheading
{INACAP}{Santiago de Chile}
{Bachelor’s degree in Computer Science}{2019 -- 2022}
\resumeSubHeadingListEnd

% technical skills
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
	\small{\item{
		\textbf{Languages}{: JavaScript, Golang, PHP, Python, C } \\
		\textbf{Frameworks}{: Next.JS, Express.JS, CodeIgniter } \\
		\textbf{Tools}{: Linux, NeoVim, Git, Docker, AWS, Apache, Nginx} \\
	}}
\end{itemize}


% experience
\section{Work Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Web Developer}{Jan. 2024 -- \bf{Present}}
{National Cancer Institute (Chile)}{Presential}
\resumeItemListStart

\resumeItem{
    Led the planning, development, and testing of
    a CodeIgniter-based API, improving development
    efficiency, ensuring data integrity, and
    standardizing information access.
}

\resumeItem{
    Migrated internal production server to Docker
    containers, optimizing the produciton and
    development environment for faster, more
    flexible deployments.
}

\resumeItem{
    Built and maintained web applications using PHP
    and CodeIgniter, integrating Oracle databases.
    Automated document generation ensuring data
    integrity and optimized query performance.
}

\resumeItem{
    Managed security tasks on local Linux servers,
    implementing measures to safeguard data and
    ensure operational continuity.
}

\resumeItemListEnd      

\resumeSubheading
{Web Developer}{Jul. 2022 -- Dec. 2023}
{Coolebra}{Remote}
\resumeItemListStart
\resumeItem{
    Development and deployment of a web scraping
    pipeline on Amazon EC2, ensuring scheduled
    data collection.
}
\resumeItem{
    Development and publication of Coolebra’s
    mobile applications on Google Play Store and
    Apple Store.
}
\resumeItem{
    Large-scale ETL data loading between
    OpenSearch and a SQL database using a
    Python-developed client.
}
\resumeItem{
    Integration of a subscription system with
    Payku and MercadoPago providers.
}
\resumeItem{
    Rewrote the entire frontend of the Coolebra
    Webpage using React and Bootstrap,
    implementing the OpenSearch search engine and
    various menu components.
}
\resumeItemListEnd      

\resumeSubheading
{Academic Tutor}{2021}
{INACAP}{RM, Santiago Centro}
\resumeItemListStart
\resumeItem{ \textbf{Programming III:} {Python, OOP and Algorithms} }\\
\resumeItem{ \textbf{Databases I:} {Design, normalization, and SQL scripting}}\\
\resumeItemListEnd

\resumeSubHeadingListEnd

% projects
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{batteryd} $|$ \emph{C}}{2024 -- Present}
\resumeItemListStart
\resumeItem{Battery state listener for OpenBSD laptops (uses apmvar library).}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{httpd} $|$ \emph{C}}{2022 -- Present}
\resumeItemListStart
\resumeItem{Small HTTP server.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{cdwn} $|$ \emph{C}}{2021 -- Present}
\resumeItemListStart
\resumeItem{CLI countdown tool.}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}

